---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
body{
  font-family: 'Arial', sans-serif;
  background-color: #FFF7F3;
  color: #C599B6;
}

h2{
  text-align: center;
  font-size: 20px;
  font-family: 
  color: #C599B6;
}

p{
  margin: auto;
  width: 50%;
  padding: 10px;
}

#text{
  font-size: 10px;
}

pre{
  text-align: center;
}
```

## This dynamic report captures trends in shoe brands and shoe colour.

```{r}
library(tidyverse)
library(magick)

#URL to my collected data
csv_file <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vQ9FjAYIcVolBBqlki61MtRaqxANC8ZIf6eiRccoxXr4eN29PoIWXS_8uF1M2Jt47MfSBrhoseDuo7L/pub?output=csv"

#Reading and renaming of my data columns
logged_data <- read_csv(csv_file)  %>%
  rename(shoe_brand = 2,
         shoe_colour = 3,
         people_count = 4,
         unique_brands = 5,
         location = 6)

#Summary values
max_unique_brands <- max(logged_data$unique_brands)

total_people <- logged_data$people_count %>% sum()

#Dynamic reporting of values
cat(paste("The maximum number of unique shoe brands in my observation are", 
      max_unique_brands, 
      "brands."))
cat(paste("The total people observed in my observation are", 
      total_people, 
      "people."))
```

This graph shows the different brands of shoes I observed, and how many of each brand I observed.

```{r}
#Bar charts
#Shoe brand bar chart
ggplot(data = logged_data) +
  geom_bar(aes(x = shoe_brand),
           fill = '#bc9bbf') + 
  labs(title = "Shoe Brand Popularity: Number of Shoes by Brand",
       x = "Brand of Shoes",
       y = "Number of Shoes")

```

It was interesting to see the many different brands of shoes whilst I was making my observations, and which brand hadthe highest number of shoes.

This graph shows the different colours of shoes I observed, and how many of each colour I observed.

```{r}
#Shoe colour bar chart
ggplot(data = logged_data) +
  geom_bar(aes(x = shoe_colour),
           fill = '#cf84bb') +
  labs(title = "Shoe Color Distribution: Number of Shoes by Colour",
       x = "Colour of Shoes",
       y = "Number of Shoes")

```

From this graph, I can see that out of the many people I observed, there weren't many wearing bright colours.

This is an animated graph showing the frequent locations which I visited and made the observations overtime. This animation shows 4 frames, each with an increasing number of data.

```{r}
frame_1 <- image_read("https://jannet-xu15.github.io/stats220/frame_1.png") %>%
  image_resize("600x400!")

frame_2 <- image_read("https://jannet-xu15.github.io/stats220/frame_2.png") %>%
  image_resize("600x400!")

frame_3 <- image_read("https://jannet-xu15.github.io/stats220/frame_3.png") %>%
  image_resize("600x400!")

frame_4 <- image_read("https://jannet-xu15.github.io/stats220/frame_4.png") %>%
  image_resize("600x400!")

animated_locations <- c(frame_1, frame_2, frame_3, frame_4)
  

image_animate(animated_locations, fps = 1)
```
